
%Section: Pubs
\sectionTitle{Publications}{\faBook}

\vspace*{.5em}
	\hspace{.5em}{\textcolor{basecolor}{\faBook} \textbf{\textsc{Refereed Journals-- Published/In Press}}}\\
	\renewcommand{\labelenumi}{[\textbf{J\arabic{enumi}}]}
	\begin{etaremune}[leftmargin=1cm]
		\item S. Bajpai, \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://ieeexplore.ieee.org/document/11320436}{Cooperative Guidance for Aerial Defense in Multiagent Systems}'', \emph{IEEE Transactions on Aerospace and Electronic Systems}, vol. 62, pp. 3700--3710, 2026.
		\item \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://doi.org/10.1109/TAES.2026.3651410}{Cooperative Target Interception in 3D Engagements Over Switched Dynamic Graphs}'', \emph{IEEE Transactions on Aerospace and Electronic Systems}, vol. 62, pp. 4181--4192, 2026.
		\item S. Kumar, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{https://arc.aiaa.org/doi/abs/10.2514/1.G008792}{Three-dimensional Nonlinear Path-following Guidance with Bounded Input Constraints}'', \emph{AIAA Journal of Guidance, Control, and Dynamics}, vol. 49, no. 1, pp. 198--215, 2026.
		\item S. Kumar, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{https://arc.aiaa.org/doi/abs/10.2514/1.G009445}{Three dimensional Trajectory Tracking for Unmanned Aerial Vehicles under Motion Constraints}'', \emph{AIAA Journal of Guidance, Control, and Dynamics}, vol. 49, no. 1, pp. 78--96, 2026.
		\item U. Siddique, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://doi.org/10.1007/s10994-025-06959-y}{Learning Fair Policies in Multi-Objective Preference-based Reinforcement Learning}'', \emph{Machine Learning Journal (MLJ)}, vol. 115, no. 23, pp. 1--34, 2026.
		\item \textbf{Abhinav Sinha}, D. Mukherjee, and S. R. Kumar, ``\href{https://ieeexplore.ieee.org/abstract/document/11018241}{Consensus-driven Deviated Pursuit for Guaranteed Simultaneous Interception of Moving Targets}'', \emph{IEEE Transactions on Aerospace and Electronic Systems}, vol. 61, no. 5, pp. 12826--12838, 2025.
		\item P. Ranjan, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://ieeexplore.ieee.org/document/10839025}{3D Guidance Law for Flexible Target Enclosing with Inherent Safety}'', \emph{IEEE Robotics and Automation Letters}, vol. 10, no. 2, pp. 2088--2095, 2025.
		\item P. Ranjan, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://ieeexplore.ieee.org/document/10660561}{Self-organizing Multiagent Target Enclosing under Limited Information and Safety Guarantees}'', \emph{IEEE Transactions on Aerospace and Electronic Systems}, vol. 61, no. 1, pp. 1066--1078, 2025.
		\item P. Ranjan, \textbf{Abhinav Sinha}, Y. Cao, D. Casbeer, and I. Weintraub, ``\href{https://ieeexplore.ieee.org/abstract/document/10634571}{Relational Maneuvering of Leader-Follower Unmanned Aerial Vehicles for Flexible Formation}'', \emph{IEEE Transactions on Cybernetics}, vol. 54, no. 10, pp. 5598--5609, 2024.
		\item \textbf{Abhinav Sinha} and S. R. Kumar, ``\href{https://asmedigitalcollection.asme.org/autonomousvehicles/article-abstract/4/3/031001/1203074/Time-Critical-Unified-Rendezvous-Guidance-for-an?redirectedFrom=fulltext}{Time-Critical Unified Rendezvous Guidance for an Unmanned Autonomous Vehicle}'', \emph{ASME Journal of Autonomous Vehicles and Systems}, vol. 4, no. 3, pp. 031001 1--8, 2024.
		\item S. Kumar, \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://www.sciencedirect.com/science/article/abs/pii/S1270963824003560}{Robust Path-following Guidance for an Autonomous Vehicle in the Presence of Wind}'', \emph{Aerospace Science and Technology}, vol. 150, pp. 109225, 2024.
		\item S. Kumar, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{https://arc.aiaa.org/doi/abs/10.2514/1.G007964}{Three-Dimensional Path Following Nonlinear Guidance for Unmanned Aerial Vehicles}'', \emph{AIAA Journal of Guidance, Control, and Dynamics}, vol. 47, no. 6, pp. 1231--1240, 2024.
		\item \textbf{Abhinav Sinha} and Y. Cao, ``\href{https://ieeexplore.ieee.org/document/10251969}{Three-Dimensional Autonomous Guidance for Enclosing a Stationary Target within Arbitrary Smooth Geometrical Shapes}'', \emph{IEEE Transactions on Aerospace and Electronic Systems}, vol. 59, no. 6, pp. 9247--9256, 2023.
		\item \textbf{Abhinav Sinha} and Y. Cao, ``\href{https://arc.aiaa.org/doi/abs/10.2514/1.G007539}{Three-Dimensional Guidance Law for Target Enclosing Within Arbitrary Smooth Shapes}'', \emph{AIAA Journal of Guidance, Control, and Dynamics}, vol. 46, no. 11, pp. 2224--2234, 2023.
		\item P. Ranjan, \textbf{Abhinav Sinha}, Y. Cao, D. Tran, D. Casbeer, and I. Weintraub, ``\href{https://arc.aiaa.org/doi/abs/10.2514/1.G007057}{Energy-efficient Ring Formation Control with Constrained Inputs}'', \emph{AIAA Journal of Guidance, Control, and Dynamics}, vol. 46, no. 7, pp. 1397--1407, 2023.
		\item \textbf{Abhinav Sinha} and Y. Cao, ``\href{https://ieeexplore.ieee.org/abstract/document/9924233}{3-D Nonlinear Guidance Law for Target Circumnavigation}'', \emph{IEEE Control System Letters}, vol. 7, pp. 655--660, 2023 (also accepted for presentation at 2023 American Control Conference, San Diego, California, USA).
		\item \textbf{Abhinav Sinha}, R. V. Nanavati, and S. R. Kumar, ``\href{https://arc.aiaa.org/doi/10.2514/1.G007122}{Three-dimensional Nonlinear Impact Time Guidance using Predicted Interception Point}'', \emph{AIAA Journal of Guidance, Control, and Dynamics}, vol. 46, no. 3, pp. 608--617, 2023.
		\item \textbf{Abhinav Sinha} and Y. Cao, ``\href{https://arc.aiaa.org/doi/10.2514/1.G006957}{Nonlinear Guidance Law for Target Enclosing with Arbitrary Smooth Shapes}'', \emph{AIAA Journal of Guidance, Control, and Dynamics}, vol. 45, no. 11, pp. 2182--2192, 2022.
		\item \textbf{Abhinav Sinha} and S. R. Kumar, ``\href{https://www.sciencedirect.com/science/article/abs/pii/S1270963822003601}{Cooperative target capture using predefined-time consensus over fixed and switching networks}'', \emph{Aerospace Science and Technology}, vol. 127, pp. 107686, 2022.
		\item \textbf{Abhinav Sinha}, S. R. Kumar, and D. Mukherjee, ``\href{https://link.springer.com/article/10.1007/s10846-022-01570-y}{Three-agent Time-constrained Cooperative Pursuit-Evasion}'', \emph{Journal of Intelligent \& Robotic Systems}, vol. 104, no. 28, pp. 1--27, 2022.
		\item \textbf{Abhinav Sinha}, S. R. Kumar, and D. Mukherjee, ``\href{https://www.sciencedirect.com/science/article/abs/pii/S1270963821007720}{Cooperative integrated guidance and control design for simultaneous interception}'', \emph{Aerospace Science and Technology}, vol. 120, pp. 107262, 2022.
	\item \textbf{Abhinav Sinha}, S. R. Kumar, and D. Mukherjee ``\href{https://doi.org/10.1016/j.ast.2021.106824}{Impact time constrained integrated guidance and control design}", \emph{Aerospace Science and Technology}, vol. 115, pp. 106824, 2021.
	\item \textbf{Abhinav Sinha}, S. R. Kumar, and D. Mukherjee ``\href{https://doi.org/10.1016/j.ast.2021.106776}{Nonsingular impact time guidance and control using deviated pursuit}", \emph{Aerospace Science and Technology}, vol. 115, pp. 106776, 2021.
	\item \textbf{Abhinav Sinha}, S. R. Kumar, and D. Mukherjee, ``\href{https://ieeexplore.ieee.org/document/9274339}{Cooperative Salvo Based Active Aircraft Defense Using Impact Time Guidance}",	\emph{IEEE Control Systems Letters}, vol. 5, no. 5, pp. 1573--1578, 2021 (also accepted for presentation at 2021 American Control Conference, New Orleans, Louisiana, USA).
	\item \textbf{Abhinav Sinha}, S. R. Kumar, and D. Mukherjee ``\href{https://arc.aiaa.org/doi/abs/10.2514/1.G005367}{Three-Dimensional Nonlinear Cooperative Salvo Using Event-Triggered Strategy}", \emph{AIAA Journal of Guidance, Control, and Dynamics}, vol. 44, no. 2, pp. 328--342, 2021.
	\item \textbf{Abhinav Sinha}, S. R. Kumar, and D. Mukherjee, ``\href{https://arc.aiaa.org/doi/abs/10.2514/1.G005180}{Three-Dimensional Guidance With Terminal Time Constraints for Wide Launch Envelops}", \emph{AIAA Journal of Guidance, Control, and Dynamics}, vol. 44, no. 2, pp. 343--359, 2021.
	\item \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://ieeexplore.ieee.org/abstract/document/9000526/}{Super-Twisting Control Based Cooperative Salvo Guidance Using Leader-Follower Approach}", \emph{IEEE Transactions on Aerospace and Electronic Systems}, vol. 56, no. 5, pp. 3556--3565, 2020.
	\item \textbf{Abhinav Sinha}, and R. K. Mishra, ``\href{https://www.tandfonline.com/doi/full/10.1080/00207179.2018.1531147}{Consensus in first order nonlinear heterogeneous multi-agent systems with event-based sliding mode control}", \emph{International Journal of Control}, vol. 93, no. 4, pp. 858--871, 2020.
	\item \textbf{Abhinav Sinha}, R. Kumar, R. Kaur and R. K. Mishra, ``\href{https://ieeexplore.ieee.org/abstract/document/8764615}{Consensus-Based Odor Source Localization by Multiagent Systems Under Resource Constraints}", \emph{IEEE Transactions on Cybernetics}, vol. 50, no. 7, pp. 3254--3263, 2020.
	\item \textbf{Abhinav Sinha}, R. Kumar, R. Kaur and A. P. Bhondekar, ``\href{https://ieeexplore.ieee.org/document/8471102}{Consensus-Based Odor Source Localization by Multiagent Systems}", \emph{IEEE Transactions on Cybernetics}, vol. 49, no. 12, pp. 4450--4459, 2019.
	\item R. K. Mishra, and \textbf{Abhinav Sinha}, ``\href{https://www.sciencedirect.com/science/article/pii/S0947358017303187}{Event-triggered sliding mode based consensus tracking in second order heterogeneous
		nonlinear multi-agent systems}", \emph{European Journal of Control}, vol. 45, pp. 30--44, 2019.
	\item T. Majumder, R. K. Mishra, \textbf{Abhinav Sinha}, S. S. Singh, and P. K. Sahu, ``\href{https://onlinelibrary.wiley.com/doi/abs/10.1002/dac.4206}{Robust congestion control in cognitive radio network using dynamic event-triggered sliding mode}", \emph{International Journal of Communication Systems}, vol. 33, no. 10, pp. e4206, 2019.
	\item \textbf{Abhinav Sinha}, and R. K. Mishra, ``\href{https://www.sciencedirect.com/science/article/pii/S0009250918302719}{Control of a nonlinear continuous stirred tank reactor via event triggered sliding modes}", \emph{Chemical Engineering Science}, vol. 187, pp. 52--59, 2018.
	\item T. Majumder, R. K. Mishra, \textbf{Abhinav Sinha}, S. S. Singh, and P. K. Sahu, ``\href{https://www.sciencedirect.com/science/article/pii/S1434841117325438}{Congestion Control in Cognitive Radio Networks with Event-triggered Sliding Mode}", \emph{AEU-- International Journal of Electronics and Communication}, vol. 90, pp. 155--162, 2018.
	\item \textbf{Abhinav Sinha}, and R. K. Mishra, ``\href{https://www.researchgate.net/publication/267637784\_Nonlinear\_autonomous\_altitude\_control\_of\_a\_miniature\_helicopter\_UAV\_based\_on\_sliding\_mode\_methodology/}{Nonlinear autonomous altitude control of miniature helicopter UAV based on sliding mode methodology}", \emph{International Journal of Electronics and Communication Technology}, vol. 61, spl.- 1, Jan- Mar 2015.
\end{etaremune}\medskip

	\hspace{.5em}{\textcolor{basecolor}{\faBook} \textbf{\textsc{Preprints}}}\\
\renewcommand{\labelenumi}{[\textbf{j\arabic{enumi}}]}
\begin{etaremune}[leftmargin=1cm]
	\item \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://arxiv.org/pdf/2606.16116}{Distributed Safe Consensus Under Asymmetric Input and Time-Varying Output Constraints}''
	\item S. Kumar, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{https://arxiv.org/pdf/2504.11592}{Provably Safe Control for Constrained Nonlinear Systems with Bounded Input}''
%	\item L. Gopikannan, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{https://arxiv.org/pdf/2509.15136}{Nonlinear Cooperative Salvo Guidance with Seeker-Limited Interceptors}''
	\item L. Gopikannan, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{https://arxiv.org/pdf/2601.07744}{Predefined-time One-Shot Cooperative Estimation, Guidance, and Control for Simultaneous Target Interception}''
\item P. K. Ranjan, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://arxiv.org/pdf/2510.06394}{Three-dimensional Integrated Guidance and Control for Leader-Follower Flexible Formation of Fixed Wing UAVs}''
\item P. K. Ranjan, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://arxiv.org/pdf/2603.23649}{Engagement-Zone-Aware Input-Constrained Guidance for Safe Target Interception in Contested Environments}''
%\item P. K. Ranjan, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://arxiv.org/pdf/2509.25053}{Safety-Critical Input-Constrained Nonlinear Intercept Guidance in Multiple Engagement Zones}''
%\item U. Siddique, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://arxiv.org/pdf/2509.20338}{Adaptive Event-Triggered Policy Gradient for Multi-Agent Reinforcement Learning}''
%\item \textbf{Abhinav Sinha}, and R. V. Nanavati, ``\href{https://arxiv.org/pdf/2509.19477}{Robust Near-Optimal Nonlinear Target Enclosing Guidance}''
%\item \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://arxiv.org/pdf/2507.01350}{Cooperative Target Capture in 3D Engagements over Switched Dynamic Graphs}''
%\item \textbf{Abhinav Sinha}, D. Mukherjee, and S. R. Kumar, ``\href{https://arxiv.org/pdf/2509.20314}{On Robustness of Consensus over Pseudo-Undirected Path Graphs}''
\end{etaremune}\medskip	


\hspace{.5em}{\textcolor{basecolor}{\faBook} \textbf{\textsc{Book Chapters}}}\\
{\renewcommand{\labelenumi}{[\textbf{BC\arabic{enumi}}]}
	\begin{etaremune}[leftmargin=1cm]
		%			\item \textbf{Abhinav Sinha}, and R. K. Mishra, ``\href{https://books.google.co.in/books?hl=en\&lr=\&id=X7sODAAAQBAJ\&oi=fnd\&pg=PA79\&ots=3FdglJwlL5\&sig=YWdwW1W3CzBhjGUbEpRlhuimLGI\#v=onepage\&q\&f=false}{Smooth sliding mode control of a nonlinear CSTR using an inverse hyperbolic function-based law}, \emph{Foundations and Frontiers in Computer, Communication and Electrical Engineering: Proceedings of 3rd International Conference C2E2}, Mankundu, West Bengal, India, 15\textsuperscript{th}-16\textsuperscript{th} Jan 2016
		%			\item T. Majumder, \textbf{Abhinav Sinha}, R. K. Mishra, S. S. Singh, and P. K. Sahu, ``\href{https://books.google.co.in/books?hl=en\&lr=\&id=X7sODAAAQBAJ\&oi=fnd\&pg=PA91\&ots=3FdglJxeP7\&sig=JO2wdGNBWvOZCrQYqJMNn5lN34o\#v=onepage\&q\&f=false}{Congestion control in Cognitive Radio Networks using fractional order rate reaching law based sliding modes}, \emph{Foundations and Frontiers in Computer, Communication and Electrical Engineering: Proceedings of 3rd International Conference C2E2}, Mankundu, West Bengal, India, 15\textsuperscript{th}-16\textsuperscript{th} Jan 2016
		\item \textbf{Abhinav Sinha}, and R. K. Mishra, ``\href{https://books.google.co.in/books?hl=en\&lr=\&id=X7sODAAAQBAJ\&oi=fnd\&pg=PA79\&ots=3FdglJwlL5\&sig=YWdwW1W3CzBhjGUbEpRlhuimLGI\#v=onepage\&q\&f=false}{Smooth sliding mode control of a nonlinear CSTR using an inverse hyperbolic function-based law}, \emph{Foundations and Frontiers in Computer, Communication and Electrical Engineering}, Taylor and Francis, 2016.
		\item T. Majumder, \textbf{Abhinav Sinha}, R. K. Mishra, S. S. Singh, and P. K. Sahu, ``\href{https://books.google.co.in/books?hl=en\&lr=\&id=X7sODAAAQBAJ\&oi=fnd\&pg=PA91\&ots=3FdglJxeP7\&sig=JO2wdGNBWvOZCrQYqJMNn5lN34o\#v=onepage\&q\&f=false}{Congestion control in Cognitive Radio Networks using fractional order rate reaching law based sliding modes}, \emph{Foundations and Frontiers in Computer, Communication and Electrical Engineering}, Taylor and Francis, 2016.
\end{etaremune}}\medskip

\hspace{.5em}{\textcolor{basecolor}{\faBook} \textbf{\textsc{Peer Reviewed Conference Proceedings}}}\\
{\renewcommand{\labelenumi}{[\textbf{C\arabic{enumi}}]}
	\begin{etaremune}[leftmargin=1cm]
		
		
		\item L. Gopikannan, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{}{Design of Exact-Time Convergent Impact Angle Guidance Laws using Trigonometric Sliding Modes}'', \emph{in Proc., 18\textsuperscript{th} International Workshop on Variable Structure Systems and Sliding Mode Control (VSS)}, Exeter, UK, 27\textsuperscript{th}-30\textsuperscript{th} Jul, 2026.
		\item L. Gopikannan, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{}{Nonlinear Cooperative Salvo Guidance with Seeker-Limited Interceptors}'', \emph{in Proc., 18\textsuperscript{th} International Workshop on Variable Structure Systems and Sliding Mode Control (VSS)}, Exeter, UK, 27\textsuperscript{th}-30\textsuperscript{th} Jul, 2026.
		\item R. V. Nanavati, \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{}{Nonlinear Control of a Fully-Actuated UAV  }'', \emph{in Proc., 18\textsuperscript{th} International Workshop on Variable Structure Systems and Sliding Mode Control (VSS)}, Exeter, UK, 27\textsuperscript{th}-30\textsuperscript{th} Jul, 2026.
		\item \textbf{Abhinav Sinha}, and R. V. Nanavati, ``\href{}{Robust Near-Optimal Nonlinear Target Enclosing Guidance}'', \emph{in Proc., 18\textsuperscript{th} International Workshop on Variable Structure Systems and Sliding Mode Control (VSS)}, Exeter, UK, 27\textsuperscript{th}-30\textsuperscript{th} Jul, 2026.
		
		\item L. Gopikannan, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{}{Cooperative Integrated Estimation-Guidance for Simultaneous Interception of Moving Targets}'', \emph{in Proc., European Control Conference (ECC)}, Reykjavík, Iceland, 7\textsuperscript{th}-10\textsuperscript{th} Jul, 2026.
			\item L. Gopikannan, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{}{Bounded-Input True Proportional Navigation for Impact-Time Control}'', \emph{in Proc., Asian Control Conference (ASCC)}, Bali, Indonesia, 17\textsuperscript{th}-21\textsuperscript{st} Jun, 2026.
		
		\item \textbf{Abhinav Sinha}, D. Mukherjee, and S. R. Kumar, ``\href{}{On Robustness of Consensus over Pseudo-Undirected Path Graphs}'', \emph{in Proc., American Control Conference (ACC)}, New Orleans, USA, 26\textsuperscript{th}-29\textsuperscript{th} May, 2026.
		\item L. Gopikannan, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{}{Trajectory Encryption Cooperative Salvo Guidance}'', \emph{in Proc., American Control Conference (ACC)}, New Orleans, USA, 26\textsuperscript{th}-29\textsuperscript{th} May, 2026.
		\item P. K. Ranjan, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{}{Safety-Critical Input-Constrained Nonlinear Intercept Guidance in Multiple Engagement Zones}'', \emph{in Proc., American Control Conference (ACC)}, New Orleans, USA, 26\textsuperscript{th}-29\textsuperscript{th} May, 2026.
		\item U. Siddique, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{}{Adaptive Event-Triggered Policy Gradient for Multi-Agent Reinforcement Learning}'', \emph{in Proc., American Control Conference (ACC)}, New Orleans, USA, 26\textsuperscript{th}-29\textsuperscript{th} May, 2026.
		\item S. Bajpai, \textbf{Abhinav Sinha}, I. Weintraub, R. Sharma, and D. Casbeer, ``\href{}{Nonlinear Guidance for a Pursuer-Turret Team for Maneuvering Target Engagement}'', \emph{in Proc., American Control Conference (ACC)}, New Orleans, USA, 26\textsuperscript{th}-29\textsuperscript{th} May, 2026.		
		
		\item S. Bajpai, P. Sood, \textbf{Abhinav Sinha}, and R. Sharma, ``\href{https://arc.aiaa.org/doi/abs/10.2514/6.2026-2346}{Terminal Time and Angle-constrained Interception of a Non-Maneuvering Target under Autopilot Lag}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 12\textsuperscript{th}-16\textsuperscript{th} Jan, 2026.
		\item S. Bajpai, \textbf{Abhinav Sinha}, and R. Sharma, ``\href{https://arc.aiaa.org/doi/abs/10.2514/6.2026-2196}{Cooperative Defense via Region-Based Interception in Turret-Evader-Pursuer Engagement}'', \emph{in Proc., Intelligent Systems Conference (AIAA SciTech Forum)}, Orlando, USA, 12\textsuperscript{th}-16\textsuperscript{th} Jan, 2026.
		\item R. Boyinine and \textbf{Abhinav Sinha}, ``\href{https://arc.aiaa.org/doi/abs/10.2514/6.2026-0122}{Observability-aided Target Interception using Bearing-only Measurements via Cooperative Estimation}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 12\textsuperscript{th}-16\textsuperscript{th} Jan, 2026.
		\item R. Sharma, \textbf{Abhinav Sinha}, and I. Weintraub, ``\href{https://arc.aiaa.org/doi/abs/10.2514/6.2026-1202}{Learning-Augmented Adaptive Guidance for Target Interception}'', \emph{in Proc., Intelligent Systems Conference (AIAA SciTech Forum)}, Orlando, USA, 12\textsuperscript{th}-16\textsuperscript{th} Jan, 2026.
		\item \textbf{Abhinav Sinha}, R. V. Nanavati, and S. R. Kumar, ``\href{https://arc.aiaa.org/doi/abs/10.2514/6.2026-0121}{Impact Time Guidance to Capture Moving Targets in the Presence of Multiple Obstacles}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 12\textsuperscript{th}-16\textsuperscript{th} Jan, 2026.
		\item S. Kumar, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{https://arc.aiaa.org/doi/abs/10.2514/6.2026-1947}{Nonlinear Path Following Guidance with Bounded Control}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 12\textsuperscript{th}-16\textsuperscript{th} Jan, 2026.
		\item R. Tabiyar, \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://arc.aiaa.org/doi/abs/10.2514/6.2026-0321}{3D Cooperative Salvo against a Stationary Target with Arbitrary Time Consensus}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 12\textsuperscript{th}-16\textsuperscript{th} Jan, 2026.
%		\item P. K. Ranjan, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{}{GPS-Denied Guidance Strategy for Safe Target Interception Under Multi-Defender Threats}'', \emph{in Proc., Intelligent Systems Conference (AIAA SciTech Forum)}, Orlando, USA, 12\textsuperscript{th}-16\textsuperscript{th} Jan, 2026.
%		\item U. Siddique, P. K. Ranjan, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{}{Deep Reinforcement Learning for Target Enclosing Under Limited Sensing and Autopilot Lag}'', \emph{in Proc., Intelligent Systems Conference (AIAA SciTech Forum)}, Orlando, USA, 12\textsuperscript{th}-16\textsuperscript{th} Jan, 2026.
		
		
		
		\item U. Siddique, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://ieeexplore.ieee.org/document/11107925}{Adaptive Event-triggered Reinforcement Learning Control for Complex Nonlinear Systems}'', \emph{in Proc., American Control Conference (ACC)}, Denver, USA, 8\textsuperscript{th}-10\textsuperscript{th} Jul, 2025.
		\item R. Boyinine, A. Chakraborty, R. Sharma, and \textbf{Abhinav Sinha}, ``\href{https://ieeexplore.ieee.org/document/11028161}{Infrastructure Planning for Multi-Vehicle Routing with Cooperative Localization}'', \emph{in Proc. 2025 IEEE/ION Position, Location and Navigation Symposium (PLANS)}, Salt Lake City, USA, 28\textsuperscript{th} Apr-1\textsuperscript{st} May, 2025.
		\item S. Bajpai, R. Boyinine, \textbf{Abhinav Sinha}, and R. Sharma, ``\href{https://doi.org/10.2514/6.2025-1547}{Toward Simultaneous Localization and Guidance for Collaborative Combat Aircraft (CCA) Effectiveness}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 6\textsuperscript{th}-10\textsuperscript{th} Jan, 2025.
		\item S. Kumar, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{https://doi.org/10.2514/6.2025-2233}{Geometric Guidance for Enclosing Moving Targets}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 6\textsuperscript{th}-10\textsuperscript{th} Jan, 2025.
		\item P. K. Ranjan, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://doi.org/10.2514/6.2025-1901}{Relational Maneuvering Guidance Strategy for Leader-Follower Flexible Formation in Three Dimensions}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 6\textsuperscript{th}-10\textsuperscript{th} Jan, 2025.
		\item S. Bandela, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://doi.org/10.2514/6.2025-1902}{A Reinforcement Learning Approach to Target Capture in the Presence of a Defender}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 6\textsuperscript{th}-10\textsuperscript{th} Jan, 2025.
		\item M. Wu, U. Siddique, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://ieeexplore.ieee.org/document/10585936}{Offline Reinforcement Learning with Failure Under Sparse Reward Environments}'', \emph{in Proc., 3rd International Conference on Computing and Machine Intelligence (ICMI)}, Mt. Pleasant (Michigan), USA, 13\textsuperscript{th}-14\textsuperscript{th} Apr, 2024.
		\item U. Siddique, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://doi.org/10.2514/6.2024-0957}{On Deep Reinforcement Learning for Target Capture Autonomous Guidance}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 8\textsuperscript{th}-12\textsuperscript{th} Jan, 2024.
		\item P. K. Ranjan, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://arc.aiaa.org/doi/10.2514/6.2024-0124}{Robust UAV Guidance Law for Safe Target Circumnavigation with Limited Information and Autopilot Lag Considerations}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 8\textsuperscript{th}-12\textsuperscript{th} Jan, 2024.
		\item \textbf{Abhinav Sinha}, D. White, and Y. Cao, ``\href{https://doi.org/10.2514/6.2024-0957}{Deep Reinforcement Learning-based Optimal Time-constrained Intercept Guidance}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 8\textsuperscript{th}-12\textsuperscript{th} Jan, 2024.
		\item S. Kumar, \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://doi.org/10.2514/6.2024-1593}{Generic Path-following Guidance for an Autonomous Vehicle}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 8\textsuperscript{th}-12\textsuperscript{th} Jan, 2024.
		\item S. Kumar, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{https://doi.org/10.2514/6.2024-0319}{Robust Nonlinear Control for Exact-time Stability of a Quadrotor UAV under Uncertainties}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 8\textsuperscript{th}-12\textsuperscript{th} Jan, 2024.
		\item R. Tabiyar, \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://ieeexplore.ieee.org/document/10442761}{Decentralized Cooperative Guidance for Time-constrained Rendezvous with Non-Accelerating Targets}'', \emph{in Proc., 9\textsuperscript{th} Indian Control Conference (ICC)}, Vishakhapatnam, India, 18\textsuperscript{th}-20\textsuperscript{th} Dec, 2023.
			\item U. Siddique, \textbf{Abhinav Sinha}, and Y. Cao, ``\href{https://icml.cc/virtual/2023/29078}{Fairness in Preference-based Reinforcement Learning}'', \emph{in 41\textsuperscript{st} International Conference on Machine Learning (ICML) Workshop : The Many Facets of Preference-Based
			Learning}, Honolulu, USA, 26\textsuperscript{th}-27\textsuperscript{th} Jul, 2023.
		\item \textbf{Abhinav Sinha} and Y. Cao, ``\href{https://ieeexplore.ieee.org/document/9924233}{Three-dimensional Nonlinear Guidance Law for Target Circumnavigation}'', \emph{in Proc., American Control Conference (ACC)}, San Diego, USA, 31\textsuperscript{st} May-2\textsuperscript{nd} Jun, 2023.
		\item \textbf{Abhinav Sinha} and Y. Cao, ``\href{https://arc.aiaa.org/doi/10.2514/6.2023-2641}{A Nonlinear Guidance Law for Target Enclosing with Arbitrary Smooth Shapes}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, National Harbor, USA, 23\textsuperscript{rd}-27\textsuperscript{th} Jan, 2023.
		\item P. K. Ranjan, \textbf{Abhinav Sinha}, Y. Cao, D. Tran, D. Casbeer, and I. Weintraub, ``\href{https://arc.aiaa.org/doi/10.2514/6.2023-2642}{Energy-efficient Ring Formation Control with Constrained Inputs}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, National Harbor, USA, 23\textsuperscript{rd}-27\textsuperscript{th} Jan, 2023.
		\item S. Kumar, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{https://arc.aiaa.org/doi/10.2514/6.2023-1055}{Robust Path-following Guidance for an Unmanned Vehicle}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, National Harbor, USA, 23\textsuperscript{rd}-27\textsuperscript{th} Jan, 2023.
		\item \textbf{Abhinav Sinha} and S. R. Kumar, ``\href{https://arc.aiaa.org/doi/10.2514/6.2023-1996}{Nonsingular Impact Time Guidance and Control Co-design against a Stationary Target}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, National Harbor, USA, 23\textsuperscript{rd}-27\textsuperscript{th} Jan, 2023.
		\item \textbf{Abhinav Sinha}, R. V. Nanavati, and S. R. Kumar, ``\href{https://arc.aiaa.org/doi/10.2514/6.2023-2496}{Three-dimensional Nonlinear Impact Time Guidance using Predicted Interception Point}'', \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, National Harbor, USA, 23\textsuperscript{rd}-27\textsuperscript{th} Jan, 2023.
		\item S. Kumar, S. R. Kumar, and \textbf{Abhinav Sinha}, ``\href{https://www.sciencedirect.com/science/article/pii/S240589632300294X}{Separate Guidance and Control Design for Autonomous Path-following}'', \emph{in Proc., 22nd IFAC International Symposium on Automatic Control in Aerospace (ACA)}, Mumbai, India, 2022.
		\item S. K. Singh, \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://www.sciencedirect.com/science/article/pii/S2405896322000970}{Nonlinear Control Design for an Unmanned Aerial Vehicle for Path Following}'', \emph{IFAC PapersOnLine}, vol. 55, no. 1, pp. 592--597, 21\textsuperscript{st}-25\textsuperscript{th} Nov, 2022.
		\item Iftisam, \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://www.sciencedirect.com/science/article/pii/S2405896322000052}{Three-dimensional Nonlinear Impact Time Guidance Accounting for Autopilot Lag}'', \emph{IFAC PapersOnLine}, vol. 55, no. 1, pp. 26--31, 2022.
		\item \textbf{Abhinav Sinha}, R. V. Nanavati, and S. R. Kumar, ``\href{https://ieeexplore.ieee.org/abstract/document/9703136}{Impact Angle Constrained Integrated Guidance and Control for a Dual-controlled Interceptor}'', \emph{in Proc., 7\textsuperscript{th} Indian Control Conference (ICC)}, Mumbai, India, 20\textsuperscript{th}-22\textsuperscript{nd} Dec, 2021.
		\item \textbf{Abhinav Sinha} and S. R. Kumar, ``\href{https://ieeexplore.ieee.org/abstract/document/9703170}{Cooperative Target Capture using Predefined-time Consensus}'', \emph{in Proc., 7\textsuperscript{th} Indian Control Conference (ICC)}, Mumbai, India, 20\textsuperscript{th}-22\textsuperscript{nd} Dec, 2021.
		\item \textbf{Abhinav Sinha}, S. R. Kumar, and D. Mukherjee, ``\href{https://ieeexplore.ieee.org/abstract/document/9482897}{Cooperative Salvo Based Active Aircraft Defense using Impact Time Guidance}'', \emph{in Proc., American Control Conference (ACC)}, New Orleans, USA, 2021.
		\item \textbf{Abhinav Sinha}, S. R. Kumar, and D. Mukherjee, ``\href{https://arc.aiaa.org/doi/abs/10.2514/6.2021-1463}{Integrated Guidance and Control For Dual Control Interceptors Under Impact Time Constraint}", \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Virtual Event, 11\textsuperscript{th}-15\textsuperscript{th} and 19\textsuperscript{th}-21\textsuperscript{st} Jan 2021.
		\item \textbf{Abhinav Sinha}, S. R. Kumar, and D. Mukherjee, ``\href{https://ieeexplore.ieee.org/abstract/document/9147854}{Three-Dimensional Nonlinear Interception Time Guidance for Stationary Targets}", \emph{in Proc., American Control Conference (ACC)}, Denver, USA, 1\textsuperscript{st}-3\textsuperscript{rd} Jul 2020.
		\item \textbf{Abhinav Sinha}, D. Mukherjee, and S. R. Kumar, ``\href{https://ieeexplore.ieee.org/abstract/document/9147677}{Deviated Pursuit based Cooperative Simultaneous Interception against Moving Targets}", \emph{in Proc., American Control Conference (ACC)}, Denver, USA, 1\textsuperscript{st}-3\textsuperscript{rd} Jul 2020.
		\item H. Bishwash, \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://www.sciencedirect.com/science/article/pii/S2405896320300343}{Deviated Pursuit Based Nonlinear Impact-Time Guidance with Finite-Time Convergence}", \emph{IFAC PapersOnLine}, vol. 53, no. 1, pp. 93--98, 2020, \textbf{Awarded Best Paper}.
		\item \textbf{Abhinav Sinha}, and S. R. Kumar, ``\href{https://arc.aiaa.org/doi/abs/10.2514/6.2020-0610}{Super-Twisting Control Based Impact Time Constrained Guidance}", \emph{in Proc., Guidance, Navigation, and Control Conference (AIAA SciTech Forum)}, Orlando, USA, 6\textsuperscript{th}-10\textsuperscript{th} Jan 2020.
		\item \textbf{Abhinav Sinha}, S. R. Kumar, and D. Mukherjee, ``\href{https://ieeexplore.ieee.org/abstract/document/9123223/}{Consensus Based Nonlinear Guidance for Cooperative Salvo}", \emph{in Proc., 6\textsuperscript{th} Indian Control Conference (ICC)}, Hyderabad, India, 18\textsuperscript{th}-20\textsuperscript{th} Dec 2019.
%		\item \textbf{Abhinav Sinha}, R. Kumar, and R. Kaur, ``Resource Efficient Control Strategy for Consensus Based Odour Source Localisation by Multiagent
%		Systems", \emph{accepted, 2018 IEEE Symposium Series on Computational Intelligence}, Bengaluru, India, 18\textsuperscript{th}-21\textsuperscript{st} Nov 2018.
		\item \textbf{Abhinav Sinha}, and R. K. Mishra, ``\href{https://ieeexplore.ieee.org/document/8529713}{Convergence of multi-agent systems to unknown source of an odor}", \emph{in Proc., 2018 IEEE 3\textsuperscript{rd} International Conference for Convergence in Technology}, Pune, India, 7\textsuperscript{th}-8\textsuperscript{th} Apr 2018.
		%\item \textbf{Abhinav Sinha}, and R. K. Mishra, ``Distributed cooperative control of multi agent systems for odor source localization", \emph{accepted, International Conference on Advances in Control and Optimization Of Dynamical Systems (ACODS 2018)}, 18\textsuperscript{th}-22\textsuperscript{nd} Feb 2018.
		\item \textbf{Abhinav Sinha}, and R. K. Mishra, ``\href{https://www.sciencedirect.com/science/article/pii/S2405896318302210}{Temperature regulation in a Continuous Stirred Tank Reactor using event triggered sliding mode control}", \emph{IFAC PapersOnLine}, vol. 51, no. 1, pp. 401--406, 2018.
		\item T. Majumder, \textbf{Abhinav Sinha}, R. K. Mishra, S. S. Singh, and P. K. Sahu, ``\href{http://ieeexplore.ieee.org/abstract/document/7438169/}{Robust nonlinear congestion controller for time delayed and uncertain cognitive radio based wireless network}", \emph{in Proc., 2015 IEEE Power, Communication and Information Technology Conference (PCITC)}, Bhubaneswar, India, 15\textsuperscript{th}-17\textsuperscript{th} Oct 2015.
		\item \textbf{Abhinav Sinha}, and R. K. Mishra, ``\href{http://ieeexplore.ieee.org/abstract/document/7192930/}{Sliding mode controller design for high performance of permanent magnet stepper motor}", \emph{in Proc., 2015 IEEE International Conference on Innovations in Information, Embedded and Communication Systems (ICIIECS)}, Coimbatore, India, 19\textsuperscript{th}-20\textsuperscript{th} Mar 2015.
		\item \textbf{Abhinav Sinha}, and R. K. Mishra, ``\href{http://ieeexplore.ieee.org/abstract/document/7192889/}{Robust altitude tracking of a miniature helicopter UAV based on sliding mode}", \emph{in Proc., 2015 IEEE International Conference on Innovations in Information, Embedded and Communication Systems (ICIIECS)}, Coimbatore, India, 19\textsuperscript{th}-20\textsuperscript{th} Mar 2015.
		\item T. Majumder, \textbf{Abhinav Sinha}, R. K. Mishra, S. S. Singh, and P. K. Sahu, ``\href{http://ieeexplore.ieee.org/abstract/document/7192909/}{Robust nonlinear congestion controller for cognitive radio based wireless network}", \emph{in Proc., 2015 IEEE International Conference on Innovations in Information, Embedded and Communication Systems (ICIIECS)}, Coimbatore, India, 19\textsuperscript{th}-20\textsuperscript{th} Mar 2015.
		\item \textbf{Abhinav Sinha}, R. K. Mishra, and S. Jaiswal, ``\href{http://ieeexplore.ieee.org/abstract/document/7155798/}{Robust and Smooth Nonlinear Control of an Industrial Robot for Automated Pick and Place}", \emph{in Proc., 2015 IEEE International Conference on Computing Communication Control and Automation (ICCUBEA)}, Pune, India, 26\textsuperscript{th}-27\textsuperscript{th} Feb 2015, \textbf{Awarded Best Paper}.
		\item \textbf{Abhinav Sinha}, P. Prasoon, P. K. Bharadwaj, and A. C. Ranasinghe , ``\href{http://ieeexplore.ieee.org/abstract/document/7053803/}{Nonlinear Autonomous Control of a Two-Wheeled Inverted Pendulum Mobile Robot Based on Sliding Mode}", \emph{in Proc., 2015 IEEE International Conference on Computational Intelligence and Networks (CINE)}, Bhubaneswar, India, 12\textsuperscript{th}-13\textsuperscript{th} Jan 2015.
		\item A. C. Ranasinghe, K. Rasnayake, \textbf{Abhinav Sinha}, and K. K. Rasnayake, ``\href{http://ieeexplore.ieee.org/abstract/document/7069566/}{Perturbing effect compensation technique for smart sensors}", \emph{in Proc., 7th IEEE International Conference on Information and Automation for Sustainability (ICIAfS)}, Colombo, Sri Lanka, 22\textsuperscript{nd}-24\textsuperscript{th} Dec 2014.
		\item \textbf{Abhinav Sinha}, and R. K. Mishra, ``\href{http://ieeexplore.ieee.org/abstract/document/6733697/}{Smooth sliding mode controller design for robotic arm}", \emph{in Proc., 2013 International Conference on Control, Automation, Robotics and Embedded Systems (CARE)}, Jabalpur, India, 16\textsuperscript{th}-18\textsuperscript{th} Dec 2013.
\end{etaremune}}\medskip		

\hspace{.5em}{\textcolor{basecolor}{\faBook} \textbf{\textsc{Others}}}\\
{\renewcommand{\labelenumi}{[\textbf{A\arabic{enumi}}]}
	\begin{etaremune}[leftmargin=1cm]
		
		\item S. Kumar, S. R. Kumar, and \textbf{Abhinav Sinha}, ``{Generalization of Path Following Problem: A Guidance Perspective}'', \emph{in Autonomous Systems and Emerging Technologies Symposium (ASSETS), Bangalore, India}, 25\textsuperscript{th}-27\textsuperscript{th} Jun 2025.
		
		\item S. Kumar, S. R. Kumar, and \textbf{Abhinav Sinha}, ``{Three-Dimensional Nonlinear Path-Following Guidance for UAVs}'', \emph{in 8\textsuperscript{th} Cyber-Physical Systems Symposium (CyPhySS), Bangalore, India}, 25\textsuperscript{th}-27\textsuperscript{th} Jul 2024.
		
		\item \textbf{Abhinav Sinha}, S. R. Kumar, and D. Mukherjee, ``\href{https://doi.org/10.36227/techrxiv.12402713.v1}{Integrated Guidance and Control Design For Time-Constrained Interception}", \emph{IEEE TechRxiv}, 2020.
		
		\item \textbf{Abhinav Sinha}, R. Kaur, R. Kumar, and A. P. Bhondekar, ``\href{https://arxiv.org/abs/1711.03819}{Cooperative control of multi-agent systems to locate source of an odor}", \emph{arXiv:1711.03819, arXiv e-prints}, 2017.
\end{etaremune}}

